full title

### 2020-11-15 paper/pldi21/related.tex
Slightly updated Relate Work

The most related previous work is the combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.  They
proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach have several
limitations compared to the dynamic shortcut.  First, they syntactically divides
a given program to \textit{applications} parts for static analysis and
\textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switching between static and dynamic and even impossible to perform both
of static and dynamic analysis to the same program part in different contexts.
Besides, they introduced \textit{mostly-concrete interpretation} similar with
our sealed symbolic execution.  However, it supports only a special
\textit{unknown} value that represents any possible value.  Thus, it cannot
preserves the precision of complex abstract domains~\cite{safe, tajs, regex,
weaklySPE} frequently used in JavaScript static analysis.  In the other hand,
the sealed symbolic execution automatically detects whether the abstract
semantics for abstract values.  Finally, \concerto preserves the soundness when
the program satisfies the \textit{state separation hypothesis}.  They assume
that states of application and framework parts do not interrogated or
manipulated by each other.  While it is reasonable for static analysis of Java
applications using external libraries, the assumption is not satisfied for
JavaScript programs in general.  Unlike their approach, our approach does not
have any assumption between static and dynamic analysis parts.

>>>>

The most related previous work is the combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.  They
proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach have several
limitations compared to the dynamic shortcut.  First, they syntactically divides
a given program to \textit{applications} parts for static analysis and
\textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switching between static and dynamic and even impossible to perform both
of static and dynamic analysis to the same program part in different contexts.
Besides, they introduced \textit{mostly-concrete interpretation} similar with
our sealed symbolic execution.  However, it supports only a special
\textit{unknown} value that represents any possible value.  Thus, it cannot
preserves the precision of complex abstract domains~\cite{revisit-recency,
regex, weaklySPE} frequently used in JavaScript static analysis.  On the other
hand, the sealed symbolic execution automatically detects whether the abstract
semantics for abstract values.  Finally, \concerto preserves the soundness when
the program satisfies the \textit{state separation hypothesis}.  They assume
that states of application and framework parts do not interrogated or
manipulated by each other.  While it is reasonable for static analysis of Java
applications using external libraries, the assumption is not satisfied for
JavaScript programs in general.  Unlike their approach, our approach does not
have any assumption between static and dynamic analysis parts.
